### 2024-05-19 fantasy-football.qmd
20240519 - capitalization

- quarterback (QB)
- running back (RB), also called halfback or tailback
- fullback (FB)
- wide receiver (WR)
- tight end (TE)
- offensive line (OL)
    - center (C)
    - offensive guard (OG)
    - offensive tackle (OT)

Quarterbacks are the most important player on the offense.
They help lead the team down the field.
Quarterbacks receive the ball from the Center at the beginning of the play, and they can either hand the ball off (typically to a running back or fullback), pass the ball (typically to a wide receiver or tight end), or run the ball.

Running backs take a hand-off from the quarterback to execute a running play.
They may also catch short passes from the quarterback or help protect (i.e., block for) the quarterback from the defensive players who are trying to tackle the quarterback.

Wide receivers catch passes from the quarterback to execute a passing play.
On running plays, they provide protection for the player running the ball (e.g., the running back) so they can get as far as possible without being tackled.

Tight ends block for running and passing plays, and they catch passes from the quarterback.

The offensive line blocks for running and passing plays.
On passing plays, they provide protection for the quarterback so the quarterback has time to pass the ball without being tackled.
On running plays, they provide protection for the player running the ball (e.g., the running back) so they can get as far as possible without being tackled.

@@

- defensive line (DL)
    - defensive end (DE)
    - defensive tackle (DT)
- linebacker (LB)
    - middle linebacker (MLB)
    - outside linebacker (OLB)
- defensive back (DB)
    - cornerback (CB)
    - safety (S)
        - free safety (FS)
        - strong safety (SS)

@@

- kicker (K)
- punter (P)
- holder
- long snapper
- punt returner
- kick returner
- and other players intended to block for or to tackle the ball carrier

@@

Other football-related situations include tackles for loss and sacks.
A tackle for loss occurs when a (non-quarterback) is tackled behind the line of scrimmage.
A sack occurs when a quarterback is tackled behind the line of scrimmage.
A pass defended occurs when a defensive back knocks down the ball in the air so that the indended receiver cannot catch the ball.

@@

A "flex position" is a flexible position that can involve a player from various positions: e.g., a running back, wide receiver, or tight end.
In fantasy football, fullbacks are classified as running backs because they both run the ball.

>>>>

- Quarterback (QB)
- Running Back (RB), also called halfback or tailback
- Fullback (FB)
- Wide Receiver (WR)
- Tight End (TE)
- Offensive Line (OL)
    - Center (C)
    - Offensive Guard (OG)
    - Offensive Tackle (OT)

Quarterbacks are the most important player on the offense.
They help lead the team down the field.
Quarterbacks receive the ball from the Center at the beginning of the play, and they can either hand the ball off (typically to a Running Back or Fullback), pass the ball (typically to a Wide Receiver or Tight End), or run the ball.

Running Backs take a hand-off from the Quarterback to execute a running play.
They may also catch short passes from the Quarterback or help protect (i.e., block for) the Quarterback from the defensive players who are trying to tackle the Quarterback.

Wide Receivers catch passes from the Quarterback to execute a passing play.
On running plays, they provide protection for the player running the ball (e.g., the running back) so they can get as far as possible without being tackled.

Tight Ends block for running and passing plays, and they catch passes from the Quarterback.

The players on the Offensive Line block for running and passing plays.
On passing plays, they provide protection for the Quarterback so the Quarterback has time to pass the ball without being tackled.
On running plays, they provide protection for the player running the ball (e.g., the running back) so they can get as far as possible without being tackled.

@@

- Defensive Line (DL)
    - Defensive End (DE)
    - Defensive Tackle (DT)
- Linebacker (LB)
    - Middle Linebacker (MLB)
    - Outside Linebacker (OLB)
- Defensive Back (DB)
    - Cornerback (CB)
    - Safety (S)
        - Free Safety (FS)
        - Strong Safety (SS)

@@

- Kicker (K)
- Punter (P)
- Holder
- Long Snapper
- Punt Returner
- Kick Returner
- and other players intended to block for or to tackle the ball carrier

@@

Other football-related situations include tackles for loss and sacks.
A tackle for loss occurs when a ball carrier is tackled behind the line of scrimmage.
A sack occurs when a Quarterback is tackled with the ball behind the line of scrimmage.
A pass defended occurs when a defensive player knocks down the ball in the air so that the indended receiver cannot catch the ball.

@@

A "flex position" is a flexible position that can involve a player from various positions: e.g., a Running Back, Wide Receiver, or Tight End.
In fantasy football, Fullbacks are classified as Running Backs because they both run the ball.
